---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Replication-Materials: When Can We Use Two-Way Fixed-Effects (TWFE): A Comparison of TWFE and Novel Dynamic Difference-in-Differences Estimators.

This repository provides all materials for replication of results in

> When Can We Use Two-Way Fixed-Effects (TWFE): A Comparison of TWFE and Novel Dynamic Difference-in-Differences Estimators.

Date: 2026-07-15

## Set up

The code for replication of the results requires the following folders: “01_Script”, “02_Data”, “03_Output”. All R Scripts are required in folder “01_Script”. Simulated data are stored in “02_Data”. The results are exported to "03_Output". Some of the scripts work with absolute file paths - please replace them in the header of the script.

Note that the simulations were performed on a high performance cluster. The respective slurm code is available in the 01_Script folder too. The results were stored in 02_Data and figures are then produced locally.

The following packages are necessary for reproduction of main results:

```{r pkgs, eval = FALSE}
library(did)
library(didimputation)
library(doParallel)
library(dplyr)
library(etwfe)
library(extrafont)
library(fect)
library(feisr)
library(foreach)
library(ggplot2)
library(ggtext)
library(grid)
library(gridExtra)
library(gridtext)
library(haven)  
library(labelled)
library(staggered)
library(tidyverse)
library(viridisLite)
```

### Scripts:

-   *01_DiD-Smulation-Program.R*: This provides the functions for the simulations.

-   *02_Setups.R*: This runs the simulations for different setups of data (Figure 2).

-   *02b_Produce-Figures_Setups.R*: Produces the respective figures from the simulated data (Figure 2).

-   *06_Run-Simulation-set_hpc_het-treat*: This runs the simulations for the main results of the paper (Figures 4-8).

-   *06b_Produce-Figures_het-treat.R*: Produces the respective figures from the simulated data (Figures 4-8).

-   *Remaining scripts*: These are robustness checks analog to main results with different parameter settings.

### Applied examples: Female earning penalty et al

The folder "04_Case-Study" contains the scripts to reproduce the examples (motherhood earnings penalty, fatherhood earnings premium, and the effect of parenthood on life satisfaction). They require access to Understanding Society UKHLS data (UKDA-6931-stata). We used Study Number 6931 - Understanding Society: Waves 1-13, 7th edition (November 2023).

Make sure to adjust the file path at the beginning of each script.

Scripts are:

-   *01_Long-UKHLS.do*: Compiles long-data format from UKHLS.

-   *02_Case_study1.R*: Analysis motherhood earnings penalty.

-   *03_Case_study2.R*: Analysis fatherhood earnings premium.

-   *04_Case_study3.R*: Analysis parental happiness.

## Version information

Version: R version 4.5.2
